Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-20 prop_iop.tex
intro

Textbook quantum mechanics asserts that, given a quantum spin system
described by the wavefunction
$\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
and the observable $S_z = \frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$ (with
post-measurement state $\fket{\ps\frac{1}{2}}$) is $\frac{\pi}{4}$ and
the probability of observing $\minus\frac{\hbar}{2}$ (with post-measurement
state $\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
frequency interpretation of probability, the above assertion implies
that when performing a very large number of experiments on quantum
systems described by wavefunction $\ket{\psi}$, a fraction
$\frac{\pi}{4}$ of the experiments will result in the observation
$\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$ will
result in the observation $\fket{\minus\frac{1}{2}}$.

In reality, i.e., in an actual experiment, simulation, or computation,
bounded by space, time, and energy resources, the situation is much
fuzzier: (i) we cannot \emph{exactly} prepare the state $\psi$; (ii)
we cannot \emph{exactly} build a measurement apparatus corresponding
to observable $S_z$; and (iii) we cannot prepare \emph{exact} replicas
of any state. In other words, we can only perform a limited number of
experiments on quantum systems closely related to wavefunction
$\ket{\psi}$ and using an apparatus that closely approximates
observable $S_z$. Given any fixed resources, these experiments will
\emph{not} result in the \emph{exact} fraction $\frac{\pi}{4}$ of
observations $\ps\frac{\hbar}{2}$ and $1-\frac{\pi}{4}$ of observations
$\minus\frac{\hbar}{2}$. Indeed, the state of the art algorithms for
computing the $n$th binary digit of~$\pi$ require on the order of
$O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
operations~\cite{journals/moc/BaileyBP97} which means that simply
referring to the $n$th digit of $\pi$ requires more and more resources
as~$n$ gets larger.

>>>>

Textbook quantum mechanics asserts that, given a quantum spin system
described by the wavefunction
$\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
and the observable $S_z = \frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$ (with
post-measurement state $\fket{\ps\frac{1}{2}}$) is $\frac{\pi}{4}$ and
the probability of observing $\minus\frac{\hbar}{2}$ (with post-measurement
state $\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
frequency interpretation of probability, the above assertion implies
that when performing a very large number of experiments on quantum
systems described by wavefunction $\ket{\psi}$, a fraction
$\frac{\pi}{4}$ of the experiments will result in the observation
$\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$ will
result in the observation $\minus\frac{\hbar}{2}$.

In reality, i.e., in an actual experiment, simulation, or computation,
bounded by space, time, and energy resources, the situation is much
fuzzier: (i) we cannot \emph{exactly} prepare the state $\psi$; (ii)
we cannot build a measurement apparatus corresponding \emph{exactly}
to observable $S_z$; and (iii) we cannot prepare \emph{exact} replicas
of any state. In other words, we can only perform a limited number of
experiments on quantum systems closely related to wavefunction
$\ket{\psi}$ and using an apparatus that closely approximates
observable $S_z$. Given any fixed resources, these experiments will
\emph{not} result in the \emph{exact} fraction $\frac{\pi}{4}$ of
observations $\ps\frac{\hbar}{2}$ and $1-\frac{\pi}{4}$ of
observations $\minus\frac{\hbar}{2}$. Indeed, the state of the art
algorithms for computing the $n$th binary digit of~$\pi$ require on
the order of $O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
operations~\cite{journals/moc/BaileyBP97} which means that simply
referring to the $n$th digit of $\pi$ requires more and more resources
as~$n$ gets larger.
